Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-18 nips_2018.tex

\begin{table}[t!]
  \makebox[\textwidth][c]{
    \scriptsize
  \tabcolsep=4pt
  \renewcommand\code\texttt
  \renewcommand\codechar[1]{\texttt{"#1"}}
  \newcommand{\helpSize}{0.25cm}
  \begin{tabular}{>{\hspace{-1em}}c<{\hspace{-1em}}>{\hspace{-2.5em}}c<{\hspace{-0.8em}}>{\hspace{-1em}}c<{\hspace{-1em}}}
    \toprule
    {\normalsize List Functions}&{\normalsize Text Editing}&{\normalsize Symbolic Regression}\\\midrule
    {\tabcolsep=4pt
      \begin{tabular}{cc}
        \begin{tabular}{c}
          \code{[7\, 0\, 2]}$\to $\code{[7\, 0\, 2\, 9]}         \\
          \code{[9\, 3]}$\to $\code{[9\, 3\, 9]} \\
          \code{$f(\ell) = $}\code{($f_1$ $\ell$ 9)}             \\
          ~                                                  \\
          ~                                                  \\
          \code{[2\, 7\, 8\, 1]}$\to $\code{8}               \\
          \hspace{0.15cm}\code{[3\, 19\, 14]}$\to $\code{19}                \\
          \code{$f(\ell) = $}\code{($f_2$ $\ell$)}
        \end{tabular}
        &
        \hspace{-0.3cm}\begin{tabular}{c}
          \code{[7\, 3]}$\to $\code{False}                              \\
          \hspace{0.3cm}\code{[3]}$\to $\code{False}                    \\
          \hspace{-0.3cm}\code{[9\, 0\, 0]}$\to $\code{True\phantom{e}} \\
          \hspace{0.3cm}\code{[0]}$\to $\code{True\phantom{e}}                        \\
          \hspace{-0.3cm}\code{[0\, 7\, 3]}$\to $\code{True\phantom{e}}                \\
          \code{$f(\ell) = $}\code{($f_3$ $\ell$ 0)}
        \end{tabular}
      \end{tabular}
    }
    &
    \hspace{-0.5cm}\begin{tabular}{c}
      +106 769-438$\to $106.769.438\\%&Nancy FreeHafer $\longrightarrow$ Dr. Nancy\\
      +83 973-831$\to $83.973.831\\
      $f(\text{\code{s}}) = $\code{(}$f_0$\code{  \codechar{.} \codechar{,} }\\
      \hspace{1.25cm}\code{($f_0$ \codechar{.} \codechar{ }}\\
      \hspace{1.4cm}\code{(cdr s)))}\\
      ~\\
      Temple Anna H $\to $TAH\\
      Lara Gregori$\to $LG\\
      $f(\text{\code{s}}) = $\code{(}$f_2$\code{ s)}\\
    \end{tabular}
    &
    \begin{tabular}{cc}
      \includegraphics[width = 3em]{figures/functions/4.png}&
      \includegraphics[width = 3em]{figures/functions/146}\\
      \code{$f($x$) = $($f_1$ x)}&    \code{$f($x$) = $($f_6$ x)}\\
      ~\\
      \includegraphics[width = 3em]{figures/functions/112.png}&
        \includegraphics[width = 3em]{figures/functions/92.png}
      \\
      \code{$f($x$) = $($f_4$ x)}&    \code{$f($x$) = $($f_3$ x)}\\

    \end{tabular}
    ~\\
    \midrule
    \hspace{1cm}\begin{tabular}{l}
      % $f_0($\code{r}$,\ell) \,=\, $\code{(foldr $\ell$ r ($\lambda$ (x a)}\\
      % \phantom{$f_0($\code{r}$,\ell) \,=\, $\code{(foldr}}\code{(cons (index (length a) $\ell$) a)))}\\
      % \hspace{\helpSize}($f_1$: \emph{Get the largest number})\\
      % $f_0(\ell) \,=\, $\code{(foldr $\ell$ 0 ($\lambda$ (x a)}\\\hspace{0.8cm}\code{ (if (> a x) a x)))}\\
      % \hspace{\helpSize}($f_1$: \emph{Get the largest number in $\ell$})\\
      %NOTE: this is the actual invention, but I removed a redundant lambda
      % below: $f_0(\ell,$\code{r}$) \,=\, $\code{(foldr r $\ell$ ($\lambda$ (x a) (cons x a)))}\\
      $f_0(\ell,$\code{r}$) \,=\, $\code{(foldr r $\ell$ cons)}\\
      \hspace{\helpSize}($f_0$: \emph{Append lists }\code{r}\emph{ and  $\ell$})\\
      $f_1(\ell,$\code{k}$) \,=\, $\code{($f_0$ (cons k nil) $\ell$)}\\
      \hspace{\helpSize}($f_1$: \emph{Append the number }\code{k}\emph{ to $\ell$})\\
      %(lambda (fold $0 0 (lambda (lambda (if (gt? $0 $1) $0 $1)))))
      $f_2(\ell) \,=\, $\code{(foldr $\ell$ 0 ($\lambda$ (x a)}\\
      \phantom{$f_2(\ell) \,=\, $}\code{(if (> a x) a x)))}\\
      \hspace{\helpSize}($f_2$: \emph{Maximum element in list $\ell$})\\
      $f_3(\ell,$\code{k}$) \,=\, $\code{(foldr $\ell$ (is-nil $\ell$)}\\
      \phantom{$f_1(\ell,$}
      \code{($\lambda$ (x a) (if a a (= k x))))}\\
      \hspace{\helpSize}($f_2$: \emph{Whether $\ell$ contains }\code{k})\\
    \end{tabular}&

>>>>

\begin{table}[t!]
  \makebox[\textwidth][c]{
    \scriptsize
  \tabcolsep=3pt
  \renewcommand\code\texttt
  \renewcommand\codechar[1]{\texttt{"#1"}}
  \newcommand{\helpSize}{0.25cm}
  \begin{tabular}{>{\hspace{-0em}}c<{\hspace{-1em}}>{\hspace{-1em}}c<{\hspace{-1em}}>{\hspace{-2.5em}}c<{\hspace{-0.8em}}>{\hspace{-1em}}c<{\hspace{-1em}}}
    \toprule
    &{\normalsize List Functions}&{\normalsize Text Editing}&{\normalsize Symbolic Regression}\\\midrule
    \rotatebox[origin=c]{90}{\normalsize \pop{Programs} \& Tasks}&{\tabcolsep=4pt
      \begin{tabular}{cc}
        \begin{tabular}{c}
          \code{[7\, 0\, 2]}$\to $\code{[7\, 0\, 2\, 9]}         \\
          \code{[9\, 3]}$\to $\code{[9\, 3\, 9]} \\
          \pop{\code{$f(\ell) = $}\code{($f_1$ $\ell$ 9)}}       \\
          ~                                                  \\
          ~                                                  \\
          \code{[2\, 7\, 8\, 1]}$\to $\code{8}               \\
          \hspace{0.15cm}\code{[3\, 19\, 14]}$\to $\code{19}                \\
          \pop{\code{$f(\ell) = $}\code{($f_2$ $\ell$)}}
        \end{tabular}
        &
        \hspace{-0.3cm}\begin{tabular}{c}
          \code{[7\, 3]}$\to $\code{False}                              \\
          \hspace{0.3cm}\code{[3]}$\to $\code{False}                    \\
          \hspace{-0.3cm}\code{[9\, 0\, 0]}$\to $\code{True\phantom{e}} \\
          \hspace{0.3cm}\code{[0]}$\to $\code{True\phantom{e}}                        \\
          \hspace{-0.3cm}\code{[0\, 7\, 3]}$\to $\code{True\phantom{e}}                \\
          \pop{\code{$f(\ell) = $}\code{($f_3$ $\ell$ 0)}}
        \end{tabular}
      \end{tabular}
    }
    &
    \hspace{-0.5cm}\begin{tabular}{c}
      +106 769-438$\to $106.769.438\\%&Nancy FreeHafer $\longrightarrow$ Dr. Nancy\\
      +83 973-831$\to $83.973.831\\
      \pop{$f(\text{\code{s}}) = $\code{(}$f_0$\code{  \codechar{.} \codechar{,} }\\
      \hspace{1.25cm}\code{($f_0$ \codechar{.} \codechar{ }}\\
      \hspace{1.4cm}\code{(cdr s)))}}\\
      ~\\
      Temple Anna H $\to $TAH\\
      Lara Gregori$\to $LG\\
      \pop{$f(\text{\code{s}}) = $\code{(}$f_2$\code{ s)}}\\
    \end{tabular}
    &
    \begin{tabular}{cc}
      \includegraphics[width = 3em]{figures/functions/4.png}&
      \includegraphics[width = 3em]{figures/functions/146}\\
      \pop{\code{$f($x$) = $($f_1$ x)}}&    \pop{\code{$f($x$) = $($f_6$ x)}}\\
      ~\\
      \includegraphics[width = 3em]{figures/functions/112.png}&
        \includegraphics[width = 3em]{figures/functions/92.png}
      \\
      \pop{\code{$f($x$) = $($f_4$ x)}}&    \pop{\code{$f($x$) = $($f_3$ x)}}\\

    \end{tabular}
    ~\\
    \midrule
    \rotatebox[origin=c]{90}{\normalsize DSL}&
    \hspace{0cm}\begin{tabular}{l}
      % $f_0($\code{r}$,\ell) \,=\, $\code{(foldr $\ell$ r ($\lambda$ (x a)}\\
      % \phantom{$f_0($\code{r}$,\ell) \,=\, $\code{(foldr}}\code{(cons (index (length a) $\ell$) a)))}\\
      % \hspace{\helpSize}($f_1$: \emph{Get the largest number})\\
      % $f_0(\ell) \,=\, $\code{(foldr $\ell$ 0 ($\lambda$ (x a)}\\\hspace{0.8cm}\code{ (if (> a x) a x)))}\\
      % \hspace{\helpSize}($f_1$: \emph{Get the largest number in $\ell$})\\
      %NOTE: this is the actual invention, but I removed a redundant lambda
      % below: $f_0(\ell,$\code{r}$) \,=\, $\code{(foldr r $\ell$ ($\lambda$ (x a) (cons x a)))}\\
      $f_0(\ell,$\code{r}$) \,=\, $\code{(foldr r $\ell$ cons)}\\
      \hspace{\helpSize}($f_0$: \emph{Append lists }\code{r}\emph{ and  $\ell$})\\
      $f_1(\ell,$\code{k}$) \,=\, $\code{($f_0$ (cons k nil) $\ell$)}\\
      \hspace{\helpSize}($f_1$: \emph{Append the number }\code{k}\emph{ to $\ell$})\\
      %(lambda (fold $0 0 (lambda (lambda (if (gt? $0 $1) $0 $1)))))
      $f_2(\ell) \,=\, $\code{(foldr $\ell$ 0 ($\lambda$ (x a)}\\
      \phantom{$f_2(\ell) \,=\, $}\code{(if (> a x) a x)))}\\
      \hspace{\helpSize}($f_2$: \emph{Maximum element in list $\ell$})\\
      $f_3(\ell,$\code{k}$) \,=\, $\code{(foldr $\ell$ (is-nil $\ell$)}\\
      \phantom{$f_1(\ell,$}
      \code{($\lambda$ (x a) (if a a (= k x))))}\\
      \hspace{\helpSize}($f_2$: \emph{Whether $\ell$ contains }\code{k})\\
    \end{tabular}&
